How predictable is extinction?

### 2018-10-24 doc/gsa2018_talk.tex
conceptual diagram made
cross validation diagram

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{figure/wiki_709px-ROC_curves}
  \end{center}

@@

@@

>>>>

  \begin{center}
    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{figure/conceptual_diagram}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.75\textheight,keepaspectratio=true]{figure/wiki_709px-ROC_curves}
  \end{center}

@@

\begin{frame}
  \frametitle{\textit{k}-fold cross-validation}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{figure/ts_cv}
  \end{center}

  \attrib{\footnotesize{Ken Williams, https://goo.gl/qLcfL8}}
\end{frame}

@@

\end{document}
